Trade-off between market and ecosystem services drives settlement decisions among smallholder ranchers in Baja California Sur, Mexico

### 2024-01-25 manuscript/manuscript.qmd
change 'binomial' to 'Bernoulli'

To evaluate the determinants of ranch occupation and population size, we rely on
two generalized linear models (GLMs). We use the first GLM to evaluate whether
market integration or local ecology has played a larger role in structuring the
distribution of occupied and abandoned ranch clusters. For this model we assume
that the dependent variable, whether a ranch cluster is occupied or abandoned,
has a binomial distribution and is related to the linear predictor by the logit
link: $$
\begin{aligned}
Y &\sim B(n, p) \\
E[Y/n] &= p \\
logit(p) &= \beta_{0} + \beta_{1} D(La\; Paz) + \beta_{2} D(Springs)
\end{aligned}
$$ with $n$ being the number of ranch clusters, $p$ the probability that a ranch
cluster is occupied, and $D(x)$ the travel time from a ranch cluster to $x$ (see
below for more details about how we calculate this).

>>>>

To evaluate the determinants of ranch occupation and population size, we rely on
two generalized linear models (GLMs). We use the first GLM to evaluate whether
market integration or local ecology has played a larger role in structuring the
distribution of occupied and abandoned ranch clusters. For this model we assume
that the dependent variable, whether a ranch cluster is occupied or abandoned,
has a Bernoulli distribution and is related to the linear predictor by the logit
link: $$
\begin{aligned}
Y &\sim B(1, p) \\
E[Y] &= p \\
logit(p) &= \beta_{0} + \beta_{1} D(La\; Paz) + \beta_{2} D(Springs)
\end{aligned}
$$ with $p$ being the probability that a ranch cluster is occupied and $D(x)$
the travel time from a ranch cluster to $x$ (see below for more details about
how we calculate this).
